A Decentralized Pub/Sub System for Trusted Machine Economy

### 2020-04-29 paper.tex
Reference our previous proposed DM

Among the challenges of data marketplace\cite{BigDataMarket}, our proposed decentralized data marketplace in\cite{MyDataMarketplace} focuses on the following issues:

\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. 1) Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilatiy control. 
\end{itemize}

>>>>

Among the challenges of data marketplace\cite{BigDataMarket}, we beleive the following four requirements and bases of a data marketplace system:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. 1) Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilatiy control. 
\end{itemize}

In contrast to centralized architectures in [CITE_centralized_DM], our proposed decentralized data marketplace \cite{MyDataMarketplace} focuses on processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfils the aforementioned requirements.
